Does Political Integration Make Cities Grow Faster?\\ Evidence From Dynastic Takeovers\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-02-23 paper/paper.tex
more lit, save progress on ID, structure paper

\title{State Size and City Growth: \\Evidence from Dynastic Takeovers}
\author{Elias Hadj Ammar}
\date{January 2023}

\begin{document}
\maketitle
\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}
Keep in mind that the title doesn't need to say everything. It needs to be catchy and it needs to be not-misleading about the core of the paper.
Alternative title ideas: 
\begin{itemize}
    \item "Good riddance? What happens to states when dynasties go extinct" - catchy, but obscure, and also not what the paper is about.
    \item "What kind of ruler makes states prosper?" "The best kind of autocrat?"
    \item ``Territory size, leaders and economic development: Evidence from German dynasties'' {Leaders, territory size and growth: Evidence from extinctions of German dynasties}

    \item "How individual dynasties in the HRE promoted or hindered growth" - to the point, but detached from literature.
    \item Good riddance
    \item Dynastic Takeovers
    \item Extinctions of Noble Families
    \item Preview of results
    \item Which country you belong to / ``When cities change hands''
    \item {Extinctions of dynasties and changes in development}
    \item {When Cities Change Hands: Extinctions of Dynasties and Changes in Development} - very clean but also detached from literature (may be fine, though)
    \item Family Affair / Family Matters / Family Business / something more fitting about families
    \item Successions and success
    \item {Family Matters: Extinctions of Dynasties and Changes in Development}
    \item something about game of thrones / a silly pun
    \item Adoptive Family / Foster Father or Evil Stepdad / In-laws
    \item Foster family or evil in-laws [only if many takeovers are by inlaws]
    \item ... of N German cities
    \item {When Cities Change Hands: Extinctions of Dynasties and \\Breaks in the Development of N German Cities}
\end{itemize}

@@

@@

Abstract: I estimate the effect of state size on development using a panel of construction events in cities of the Holy Roman Empire. I exploit variation from lineage extinctions, which caused cities to become part of different lineages' territorial holdings. I find that X. I discuss economic mechanisms that explain this effect.

@@

I use a generalised difference-in-differences framework with varying intensity of treatment. The treatment is the size difference between the old and the new rulers' territorial holdings. I will argue that the takeover constitutes a shock to territory size that is exogenous to development. I support this argument using an event study, showing that cities with different takeover experiences did not differ in growth (conditional on city and year fixed effects) before their respective takeovers.

@@

@@

>>>>

\title{Does Political Integration Make Cities Grow Faster?\\
Evidence From Dynastic Takeovers\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}
}
\author{Elias Hadj Ammar}
\date{January 2023}

\begin{document}
\maketitle

\begin{abstract}
I use historical data on construction activity and territorial history to estimate the effect of state size on city growth in the Holy Roman Empire. I exploit variation from lineage extinctions, which caused cities to become part of different lineages' territorial holdings. I find that an X\% increase in territory size is associated with a Y\% increase in construction activity.
\end{abstract}

Keep in mind that the title doesn't need to say everything. It needs to be catchy and it needs to be not-misleading about the core of the paper.
Alternative title ideas: 
\begin{itemize}
    \item "Good riddance? What happens to states when dynasties go extinct" - catchy, but obscure, and also not what the paper is about.
    \item "What kind of ruler makes states prosper?" "The best kind of autocrat?"
    \item ``Territory size, leaders and economic development: Evidence from German dynasties'' {Leaders, territory size and growth: Evidence from extinctions of German dynasties}

    \item "How individual dynasties in the HRE promoted or hindered growth" - to the point, but detached from literature.
    \item Dynastic Takeovers
    \item Extinctions of Noble Families
    \item Preview of results
    \item Which country you belong to / ``When cities change hands''
    \item {Extinctions of dynasties and changes in development}
    \item {When Cities Change Hands: Extinctions of Dynasties and Changes in Development} - very clean but also detached from literature (may be fine, though)
    \item Family Affair / Family Matters / Family Business / something more fitting about families
    \item Successions and success
    \item Power and prosperity
    \item {Family Matters: Extinctions of Dynasties and Changes in Development}
    \item something about game of thrones / a silly pun
    \item Adoptive Family / Foster Father or Evil Stepdad / In-laws
    \item Foster family or evil in-laws [only if many takeovers are by inlaws]
    \item ... of N German cities
    \item {When Cities Change Hands: Extinctions of Dynasties and \\Breaks in the Development of N German Cities}
    \item {State Size and City Growth: Evidence from Dynastic Takeovers}
    \item {Political Integration and Growth: \\Evidence from Dynastic Takeovers}
    \end{itemize}

@@

\doublespacing

@@

@@

I use a stacked event study framework with varying intensity of treatment. The treatment is the size difference between the old and the new rulers' territorial holdings. I will argue that the takeover constitutes a shock to territory size that is exogenous to development. The event study shows that cities with different takeover experiences did not differ in growth (conditional on city and year fixed effects) before their respective takeovers.

@@

\section{Cities, lineages, and territories}

\section{Empirical approach}

\subsection{Pooled OLS regression}

\subsection{Obtaining a dataset of stacked natural experiments}

\subsection{Stacked event study and extinction IV}

\section{Results}

\section{Validity and robustness}

\section{Conclusion}

@@

\newpage
\section*{Tables and figures}
